### 2018-06-29 Risk estimation/risk-estim.tex
Drafty but complete risk estimation

\usepackage[showonlyrefs]{mathtools}
%\usepackage{autonum}

@@

% Macros
\DeclareMathOperator*{\argmin}{argmin}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\one}{\mathbf{1}}
%\renewcommand{\S}{\mathcal{S}}
\newcommand{\Expect}[1]{\E\left[#1\right]}
\newcommand{\given}{\mbox{ }\vert\mbox{ }}
\renewcommand{\hat}{\widehat}
\DeclareMathOperator*{\trace}{tr}
\DeclareMathOperator*{\diag}{diag}
\renewcommand{\tilde}{\widetilde}
\newcommand{\Expectwrt}[2]{\mathbb{E}_{ #1 }\left[ #2 \right]}
\usepackage{xspace}
\makeatletter
\newcommand*{\iid}{%
    \@ifnextchar{.}%
        {i.i.d.}%
        {i.i.d.\@\xspace}%
}
\makeatother

\newcommand{\Pnd}{P_{\mathcal{N}(D)}}

\newtheorem{result}{Result}
\newtheorem{theorem}{Theorem}[result]
\renewcommand*{\sectionautorefname}{Section}%

@@

@@

Suppose we are minimizing the negative log likelihood from a natural
exponential family subject to the generalized lasso penalty. That is,
given $Y_i \sim p(y \given \eta_i(\tau))$ for $\tau \in \R^p$, $i=1,\ldots,n$, our goal is to solve
\begin{equation}
  \label{eq:1}
  \hat\tau = \argmin_\tau \sum_{i=1}^n \phi(\eta_i(\tau)) - \langle y_i,\
  \eta_i(\tau)\rangle + \lambda\norm{D\tau}_1,
\end{equation}
where $D\in \R^{q\times p}$.

This generalizes the various standard models. For example,
$\ell_1$-trend filtering has $\phi(x) = x^2/2$, $\eta_i(x)=x_i$, and
$D$ the first-order discrete difference operator. Variance estimation
in our context has $\phi(x) = x$, $y_i = z^2_i$ (where $z_i\sim
N(0,\exp(-h)$) and $\eta_i(x) = -e^{-\tau_i}$. Logistic loss also
falls into this category.

We first consider the case that $\eta_i(\tau) = \eta_i(\tau_i)$, i.e.,
$\tau \in \R^n$ and $p(y_i \given \tau) = p(y_i \given \tau_i)$.

\begin{theorem}
  The divergence of $\hat\tau(y)$ is given by
  \begin{equation}
    \label{eq:2}
    \trace\left(D \hat\tau(y)\right) = -\Pnd \left(\Pnd
      \diag\left(\frac{d^2}{d\tau_i^2}\ell
        \vert_{y_i,\hat{\eta}_i}\right) \Pnd\right)^\dagger \Pnd
      \diag\left(\frac{d^2}{d\tau_i d y_i} \ell \vert_{y_i,\hat{\eta}_i}\right),
    \end{equation}
    where $\ell = \ell(y,\eta(\tau_i)) = \sum_{i=1}^n \phi(\eta_i(\tau_i)) - \langle y_i,\
    \eta_i(\tau_i)\rangle$, $\hat{\eta_i} = \eta_i(\hat\tau_i)$, and 
    \begin{equation}
      \label{eq:3}
      \Pnd = I_n - D_S^\top (D_S^\top D_S)^\dagger D_S
    \end{equation}
    is the projection onto the null-space of $D_S$, where $S = \{j \in
    [q] : D\hat\tau = 0\}$, and the notation $D_S$ means the rows of
    $D$ whose indices are in $S$.
\end{theorem}

\paragraph{Special cases:}
\begin{enumerate}
\item If we are interested in the natural exponential family (that is
  $\eta_i(\tau_i)=\tau_i$), then $\frac{d^2}{d\tau_i d y_i} \ell = -1$
  and $\frac{d^2}{d\tau_i^2}\phi_i(\eta_i(\tau_i)) = \textrm{Var}[y_i]$.
\item For Gaussian likelihood, $\frac{d^2}{d\tau_i^2}\ell = 1$
  and $\frac{d^2}{d\tau_i d y_i} \ell = -1$, so the divergence is the
  dimension of $\mathcal{N}(D_S)$ as shown in
  \citet{TibshiraniTaylor2012}. 
\item For logistic loss, $\frac{d^2}{d\tau_i^2}\ell =
  e^{\tau_i}/(1+e^{\tau_i})^2$ and 
  $\frac{d^2}{d\tau_i d y_i} \ell = -1$.
\item For the case of variance estimation, we have $\frac{d^2}{d\tau_i^2}\ell =
  y^2_ie^{-h}$ and 
  $\frac{d^2}{d\tau_i d y_i} \ell = -e^{-h}$.
\end{enumerate}

Now we generalize to the regression setting. Define
$\mu_i = x_i^\top \beta$. Furthermore, write
\begin{equation}
  \label{eq:4}
  \hat\beta = \argmin_\tau \sum_{i=1}^n \phi(\mu_i(\beta)) - \langle y_i,\
  \mu_i(\beta)\rangle + \lambda\norm{D\beta}_1.
\end{equation}

\begin{theorem}
  The divergence of $\hat\mu(y)$ is given by
  \begin{equation}
    \label{eq:5}
    \trace\left(D \hat\mu(y)\right) = -X_P \left(X^\top_P
      \diag\left(\frac{d^2}{d\mu_i^2}\ell
        \vert_{y_i,\hat{\mu}_i}\right) X_P\right)^\dagger X^\top_P
      \diag\left(\frac{d^2}{d\mu_i d y_i} \ell \vert_{y_i,\hat{\mu}_i}\right),
    \end{equation}
    where $\ell = \ell(y,\eta(\mu_i)) = \sum_{i=1}^n \phi(\eta_i(\mu_i)) - \langle y_i,\
    \mu_i\rangle$, $\hat{\eta_i} = \eta_i(x_i^\top\hat\beta)$, and 
    \begin{equation}
      \label{eq:6}
      X_P =( I_n - D_S^\top (D_S^\top D_S)^\dagger D_S) X
    \end{equation}
    is the projection of $X$ onto the null-space of $D_S$.
\end{theorem}

@@

>>>>

%\usepackage{autonum}

@@

% Macros
\DeclareMathOperator*{\argmin}{argmin}
\newcommand{\norm}[1]{\left\lVert #1 \right\rVert}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\one}{\mathbf{1}}
%\renewcommand{\S}{\mathcal{S}}
\newcommand{\Expect}[1]{\E\left[#1\right]}
\newcommand{\given}{\mbox{ }\vert\mbox{ }}
\renewcommand{\hat}{\widehat}
\DeclareMathOperator*{\trace}{tr}
\DeclareMathOperator*{\Cov}{Cov}
\DeclareMathOperator*{\diag}{diag}
\renewcommand{\tilde}{\widetilde}
\newcommand{\Expectwrt}[2]{\mathbb{E}_{ #1 }\left[ #2 \right]}
\usepackage{xspace}
\makeatletter
\newcommand*{\iid}{%
    \@ifnextchar{.}%
        {i.i.d.}%
        {i.i.d.\@\xspace}%
}
\makeatother

\newcommand{\Pnd}{P_{\mathcal{N}(G)}}

\usepackage{aliascnt}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newaliascnt{lemma}{theorem}
\newtheorem{lemma}[lemma]{Lemma}
\aliascntresetthe{lemma}
\providecommand*{\lemmaautorefname}{Lemma}
\newaliascnt{cor}{theorem}
\newtheorem{corollary}[cor]{Corollary}
\aliascntresetthe{cor}
\providecommand*{\corautorefname}{Corollary}
\newaliascnt{def}{theorem}
\newtheorem{definition}[def]{Definition}
\aliascntresetthe{def}
\providecommand*{\defautorefname}{Definition}
\newtheorem{example}{Example}

@@

\usepackage{mathtools}
\mathtoolsset{showonlyrefs}

@@

Consider a random vector $Y \in \R^n$ with distribution in the
exponential family with independent
components. Specifically, write the density of $Y$ as
\begin{equation}
  \label{eq:4}
  p(Y \given \theta) = \left(\prod_{i=1}^n h(y_i)\right)\exp\left\{
    \sum_{i=1}^n w(y_i) \mu_i(\theta) -\psi_i(\theta) \right\}.
\end{equation}
We will consider estimation of $\theta$ subject to the generalized lasso penalty. That is,
our goal is to solve 
\begin{equation}
  \label{eq:1}
  \hat\theta(y) = \argmin_\theta \ell(y | \theta) +
  \lambda\norm{G\theta}_1 = \argmin_\theta\sum_{i=1}^n \psi_i(\theta) - w(y_i)\mu_i(\theta) + \lambda\norm{G\theta}_1,
\end{equation}
where $G\in \R^{q\times p}$ and $\theta\in\R^p$.

This generalizes many standard models. For example,
$\ell_1$-trend filtering has $p=n$, $\psi_i(x) = x_i^2/2$,
$\mu_i(x)=x_i$, $w(x)=2$, and
$G$ the first-order discrete difference operator. Variance estimation
in our context has $\psi_i(x) = x_i$, $w(x) = y^2_i$ and $\mu_i(x) = e^{-x_i}$. Logistic loss also
falls into this category. We use $G$ rather than the more common
choice of $D$ to avoid confusion with the differential operator that
we will require below.

\paragraph{Notation} For a vector-valued function $f:\R^p\rightarrow
\R^q$, we use the notation $Df$ to denote the Jacobian matrix
and $\nabla f$ to be the gradient.

We first consider the case that $\theta \in\R^n$ and that $\psi_i$ and
$\mu_i$ operate component-wise on
$\theta$. That is $p(y \given \theta) = \prod_{i=1}^n p(y_i \given \theta_i)$.

\begin{theorem}
\label{thm:simple-divergence}
  Suppose $p(y \given \theta) = \prod_{i=1}^n p(y_i \given \theta_i)$
  and that $\hat{\theta}$ is a solution of \eqref{eq:1}. Then, the
  divergence of $\hat\theta(y)$ is given by 
  \begin{equation}
    \label{eq:2}
    \trace\left(D \hat\theta(y)\right) = -\Pnd \left(\Pnd
      \diag\left(\frac{d^2}{d\theta_i^2}\ell
        \bigg\vert_{y_i,\hat{\theta}_i}\right) \Pnd\right)^\dagger \Pnd
      \diag\left(\frac{d^2}{d\theta_i d y_i} \ell \bigg\vert_{y_i,\hat{\theta}_i}\right),
    \end{equation}
    where 
    \begin{equation}
      \label{eq:3}
      \Pnd = I_n - G_S^\top (G_S^\top G_S)^\dagger G_S
    \end{equation}
    is the projection onto the null-space of $G_S$, where $S = \{j \in
    [q] : G\hat\theta = 0\}$, and the notation $G_S$ means the rows of
    $G$ whose indices are in $S$.
\end{theorem}

\paragraph{Special cases:}
\begin{enumerate}
\item If we are interested in the natural exponential family (that is
  $\mu_i(\theta)=\theta_i$ and $w(y_i)=y_i$), then $\frac{d^2}{d\theta_i d y_i} \ell = -1$
  and $\frac{d^2}{d\theta_i^2}\psi_i(\theta_i) = \textrm{Var}[Y_i]$.
\item In particular, if $p(y_i \given \theta_i) = \mbox{N}(\theta_i, \sigma^2)$, then $\frac{d^2}{d\theta_i^2}\ell = \sigma^2$
  and $\frac{d^2}{d\tau_i d y_i} \ell = -1$, so the divergence is
  $\sigma^2$ times the
  dimension of $\mathcal{N}(G_S)$ as shown in
  \citet{TibshiraniTaylor2012}. 
\item For logistic loss, $\frac{d^2}{d\theta_i^2}\ell =
  e^{\theta_i}/(1+e^{\theta_i})^2$ and 
  $\frac{d^2}{d\tau_i d y_i} \ell = -1$.
\item For the case of variance estimation, we have $\frac{d^2}{d\theta_i^2}\ell =
  y^2_ie^{-\theta}$ and 
  $\frac{d^2}{d\theta_i d y_i} \ell = -e^{-\theta}$.
\end{enumerate}

Now we generalize to the regression setting. Define
$\theta_i = x_i^\top \beta$, $\beta \in \R^p$. And let
\begin{equation}
  \label{eq:7}
   \hat\beta(y) = \argmin_\beta \sum_{i=1}^n \psi_i(x_i^\top \beta) -
   w(y_i)\mu_i(x_i^\top \beta) + \lambda\norm{G\beta}_1,
\end{equation}

\begin{theorem}
\label{thm:regression-divergence}
  The divergence of $\hat\theta(y) := X\hat\beta(y)$ is given by
  \begin{equation}
    \label{eq:5}
    \trace\left(D \hat\theta(y)\right) = -X_P \left(X^\top_P
      \diag\left(\frac{d^2}{d\theta_i^2}\ell
        \bigg\vert_{y_i,\hat{\theta}_i}\right) X_P\right)^\dagger X^\top_P
      \diag\left(\frac{d^2}{d\theta_i d y_i} \ell \bigg\vert_{y_i,\hat{\theta}_i}\right),
    \end{equation}
    where 
    \begin{equation}
      \label{eq:6}
      X_P =( I_n - G_S^\top (G_S^\top G_S)^\dagger G_S) X
    \end{equation}
    is the projection of $X$ onto the null-space of $G_S$.
\end{theorem}

@@

\section{Risk estimation}
\label{sec:risk-estimation}

If $Y \sim \mbox{N}(\theta, \sigma^2)$, a now common method of risk
estimation makes use of Stein's Lemma.
\begin{lemma}[Stein's Lemma]
  Assume $f(Y)$ is weakly differentiable with essentially
  bounded weak partial derivatives on $\R^n$, then
  \begin{equation}
    \label{eq:8}
    \trace \Cov(Y,f(Y)) = \Expect{\left\langle Y,\ f(Y)\right\rangle} = \sigma^2\Expect{\trace Df(Y) \bigg\vert_y }.
  \end{equation}
\end{lemma}
The utility of this result comes from examining the decomposition of
the mean squared error of $f(Y)$ as an estimator of $\theta$.
\begin{align}
  \label{eq:9}
  \Expect{\norm{\theta-f(Y)}_2^2} 
  &= \Expect{\norm{Y-f(Y)}} -n\sigma^2 + 2
    \trace\Cov(Y,f(Y))\\
  &= \Expect{\norm{Y-f(Y)}} -n\sigma^2 + 2\sigma^2
    \Expect{\trace Df(y) \bigg\vert_Y} .
\end{align}
This characterization motivates the definition of degrees-of-freedom
for linear predictors ($\textrm{df} :=\frac{1}{\sigma^2} \trace
Df(y)\big\vert_Y$)~\citep{efron1986biased}, where $f(y)=Hy$. Using 
Stein's Lemma, assuming $\sigma^2$ is known, we have Stein's Unbiased
Risk Estimator
\begin{equation}
  \label{eq:10}
  SURE_\theta = \norm{Y-f(Y)} -n\sigma^2 + 2\sigma^2\trace Df(y) \bigg\vert_y.
\end{equation}
Note that this is a risk for estimating the $n$-dimensional parameter $\theta$.

The following result generalizes this idea to certain continuous
exponential families.
\begin{lemma}[Generalized Stein Lemma~\citep{Eldar2009}]
  \label{thm:g-stein-lemma}
  Assume $f(Y)$ is weakly differentiable with essentially
  bounded weak partial derivatives on $\R^n$. Let $Y$ be distributed
  according to a natural exponential family
  \begin{equation}
    \label{eq:11}
    p(Y \given \beta) = \left(\prod_{i=1}^n h(y_i)\right)\exp\left\{
    \sum_{i=1}^n y_i \theta_i(\beta_i) -\psi(\beta_i) \right\},
  \end{equation}
  and assume that $h$ is weakly differentiable and that $\theta_i$ is
  one-to-one. Then,
  \begin{equation}
    \label{eq:12}
    \Expect{\left\langle \theta(\beta),\ f(Y)\right\rangle} = - \Expect{
      \left\langle\frac{\nabla h(Y)}{h(Y)},\ f(Y)\right\rangle + \trace Df(y) \bigg\vert_Y}.
  \end{equation}
Note that $\nabla h(Y)$ here means the vector $[d/dy h(y)
\vert_{y_i}]$ and $h(Y)$ means the vector $[h(y_i)]$.
\end{lemma}
Therefore we define the Generalized SURE~\citep{Eldar2009} along the lines of the multivariate Gaussian case.
\begin{lemma}
  \label{lem:gsure}
  Assume $h$ and $\nabla h$ are weakly differentiable, $\theta_i$ is one-to-one,
  $f(Y)$ is weakly differentiable with essentially bounded partial
  derivatives and that $p(Y\given\beta)$ is as in \eqref{eq:11}. Then
  \begin{equation}
    \label{eq:13}
    GSURE_{\theta} = \norm{f(Y)}^2_2 + 2 \left\langle\frac{\nabla
        h(Y)}{h(Y)},\ f(Y)\right\rangle + 2\trace Df(y) \bigg\vert_Y +
    \frac{1}{h(Y)} \trace \frac{\partial^2 h(y)}{\partial y^2}\bigg\vert_Y
  \end{equation}
  is an unbiased estimator for the MSE of an estimator $f(Y)$ of
  $\theta$: $\Expect{\norm{f(Y) - \theta(\beta)}_2^2}$.
\end{lemma}

\begin{proof}
  We have
  \begin{align}
    \label{eq:14}
    \Expect{\norm{f(Y) - \theta(\beta)}_2^2} 
    &= \Expect{\norm{f(Y)}_2^2} + \Expect{\norm{\theta}_2^2} -
      2\Expect{\left\langle \theta(\beta),\ f(Y)\right\rangle}.
  \end{align}
  Now, the first term is a function of the data only, and to the last term, we simply apply
  \autoref{thm:g-stein-lemma}. For the second term,
  \begin{align}
    \Expect{\norm{\theta}_2^2} 
    &=\Expect{\langle \theta,\ \theta \rangle}
     = -\Expect{\left\langle\frac{\nabla h(Y)}{h(Y)},\ \theta\right\rangle}\\ 
    &= \Expect{\left\langle\frac{\nabla h(Y)}{h(Y)},\
      \frac{\nabla h(Y)}{h(Y)}\right\rangle} + \Expect{\trace
      \frac{\partial}{\partial y} \frac{\nabla h(y)}{h(y)}
      \bigg\vert_Y}\\
    &= \Expect{\frac{\norm{\nabla h(Y)}_2^2}{h(Y)^2}} + \Expect{\trace
      \frac{\norm{\nabla h(Y)}_2^2 +h(Y) \partial^2/\partial y^2 h(y)\big\vert_Y} 
      {h(Y)^2}}\\ 
    &=\Expect{ \frac{1}{h(Y)} \trace \frac{\partial^2 h(y)}{\partial y^2}\bigg\vert_Y},
  \end{align}
  by applying \autoref{thm:g-stein-lemma} twice along with the
  quotient rule.
\end{proof}

\begin{theorem}
  Let $Y_i \sim N(0, e^{x_i})$. Consider estimating $x$ by solving
  \begin{equation}
    \label{eq:15}
    \min_h \sum_{i=1}^n x_i + y_i^2e^{-x_i} + \lambda \norm{Gx}_1.
  \end{equation}
  Then an unbiased estimator of $\Expect{\norm{\frac{1}{2e^x} -
      \frac{1}{2e^{\hat x}}}}_2^2$ is given by
  \begin{equation}
    \label{eq:16}
    \norm{\frac{1}{2e^{\hat x}}}_2^2 - \frac{1}{2}\left\langle
      \frac{1}{y^2},\ \frac{1}{e^{\hat x}}\right\rangle + 2 \Pnd \left(\Pnd
      \diag\left(y^2e^{-\hat x}\right) \Pnd\right)^\dagger \Pnd
      \diag\left( e^{-\hat x}\right) + \frac{3}{4y^4},
  \end{equation}
where $\Pnd$ is as in \eqref{eq:3}.
\end{theorem}

\begin{proof}
  Define $z_i := y_i^2$ and $\theta_i = -\frac{1}{2e^{x_i}}$. Then
  \begin{align}
    \label{eq:17}
    p(z_i \given x_i) 
    &= \frac{1}{\sqrt{2\pi z_i e^{x_i}}} \exp\left\{-\frac{1}{2}
      \frac{z_i}{e^{x_i}}\right\}\one_{(0,\infty)}(z_i)\\
    &= \frac{1}{\sqrt{\pi z}}\one_{(0,\infty)}(z_i) \exp\left\{z_i \cdot
      \left(-\frac{1}{2e^{x_i}}\right) -
      \left(-\frac{1}{2}\log\left(\frac{1}{2 e^{x_i}}\right)
      \right)\right\}\\
    &= \frac{1}{\sqrt{\pi z}}\one_{(0,\infty)}(z_i)
      \exp\left\{z_i\cdot \theta_i - \psi(\theta_i)\right\},
  \end{align}
  which is a natural exponential family with $\psi(t) =
  -\frac{1}{2}\log(-t)$ and $h(t) = \frac{1}{\sqrt{\pi t}}
  \one_{(0,\infty)}(t)$. Therefore, $d/dt \log h(t) = -1/(2t)$ and
  $(d^2/dt^2 h(t))/h(t) = 3 / (4t^2)$. Finally, we have $\frac{d^2}{d\theta_i^2}\ell =
  y^2_ie^{-\theta}$ and 
  $\frac{d^2}{d\theta_i d y_i} \ell = -e^{-\theta}$. The result
  follows from \autoref{thm:simple-divergence} and \autoref{lem:gsure}.

\end{proof}

An alternate model selection technique is to examine the
Kullback-Leibler Divergence between the density under
$\theta=\hat\theta(Y)$ and that under $\theta=\theta$:
$\Expect{KL(p(Y\given \hat\theta(Y)) \Vert p(Y\given \theta))}$. For
exponential families, we have
\begin{equation}
\Expect{KL(\hat\theta(Y) \Vert 
  \theta)} = \Expect{KL(p(Y\given \hat\theta(Y)) \Vert p(Y\given
  \theta))} = \left\langle \hat\theta(Y)-\theta,\ \nabla
  \psi(\hat\theta(Y))\right\rangle + \psi(\theta) - \psi(\hat\theta(Y)).
\end{equation}

An application of \autoref{thm:g-stein-lemma} thus provides an
unbiased estimator of this quantity~\citep{Deledalle2017}.
\begin{lemma} 
  \label{lem:sukls}
  Assume $h$ and $\nabla h$ are weakly differentiable, $\theta_i$ is one-to-one,
  $f(Y)$ is weakly differentiable with essentially bounded partial
  derivatives and that $p(Y\given\beta)$ is as in \eqref{eq:11}. Then
  \begin{equation}
    SUKLS = \left\langle \hat\theta + \frac{\nabla h(Y)}{h(Y)},\
      \nabla \psi(\hat\theta(Y))\right\rangle + \trace Df(y) \bigg\vert_Y
    - \psi(\hat\theta(Y))
  \end{equation}
  is unbiased for $\Expect{KL(\hat\theta(Y) \Vert
  \theta)} - \psi(\theta)$.
\end{lemma}

\begin{corollary}
   Let $Y_i \sim N(0, e^{x_i})$. Consider estimating $x$ by solving
  \begin{equation}
    \label{eq:15}
    \min_h \sum_{i=1}^n x_i + y_i^2e^{-x_i} + \lambda \norm{Gx}_1.
  \end{equation}
  Then an unbiased estimator of $\Expect{KL(\hat x \Vert
    x} - \psi(\theta)$ is given by
  \begin{equation}
    \label{eq:18}
    -\frac{n}{2} - \left\langle \frac{1}{2y^2},\ e^{\hat
        x}\right\rangle + 
    -\frac{1}{2}\log\left(2e^{\hat
        x_i}\right) + \Pnd \left(\Pnd
      \diag\left(y^2e^{-\hat x}\right) \Pnd\right)^\dagger \Pnd
      \diag\left( e^{-\hat x}\right). 
  \end{equation}
\end{corollary}
\begin{proof}
  As $\hat \theta_i = -\frac{1}{2e^{\hat x_i}}$, 
  \[
    \psi(\hat\theta_i) = -\frac{1}{2}\log\left(\frac{1}{2e^{\hat
          x_i}}\right)
  \]
  and $d/d\theta \psi(\theta) = -\frac{1}{2\theta}$. Thus
  \begin{align}
    SUKLS 
    &= \left\langle -\frac{1}{2e^{\hat x}} - \frac{1}{2y^2},\ e^{\hat
      x}\right\rangle + \trace Df(y) \bigg\vert_Y
      +\frac{1}{2}\log\left(\frac{1}{2e^{\hat
      x_i}}\right)\\
    &= -\frac{n}{2} - \left\langle \frac{1}{2y^2},\ e^{\hat
      x}\right\rangle + \trace Df(y) \bigg\vert_Y
      -\frac{1}{2}\log\left(2e^{\hat
      x_i}\right).
  \end{align}
NOTE: I think some signs are wrong here.
\end{proof}
